Lucid: Lifting-based Uncertain Control Invariant Dynamics

### 2025-07-28 docs/paper/figures/architecture.tex
chore: add benchmark template

\begin{figure}
    \centering
    \begin{tikzpicture}[node distance=0.6cm and 0.6cm,
            input-block/.style={rectangle, draw, fill=red!10, text width=2.5cm, minimum height=0.8cm, align=center, rounded corners},
            output-block/.style={rectangle, draw, fill=green!20, text width=2.6cm, minimum height=0.8cm, align=center, rounded corners},
            block/.style={rectangle, draw, fill=accent!20, text width=2.0cm, minimum height=0.8cm, align=center, rounded corners},
            arrow/.style={thick,->,>=latex},
            % tool/.style={rectangle, draw, fill=magenta!10, text width=3cm, minimum height=0.8cm, align=center, rounded corners},
            inv/.style={}
        ]

        % Input block
        \node[doc] (input) {Config\\(.yaml?)};

>>>>

\begin{figure}
    \centering
    \begin{tikzpicture}[node distance=0.6cm and 0.6cm,
            input-block/.style={rectangle, draw, fill=red!10!white, text width=2.5cm, minimum height=0.8cm, align=center, rounded corners, drop shadow=gray!50},
            output-block/.style={rectangle, draw, fill=green!20!white, text width=2.6cm, minimum height=0.8cm, align=center, rounded corners, drop shadow=gray!50},
            block/.style={rectangle, draw, fill=accent!20!white, text width=2.0cm, minimum height=0.8cm, align=center, rounded corners, drop shadow=gray!50},
            arrow/.style={thick,->,>=latex},
            doc/.style={draw,thick,align=center,color=black,shape=document,minimum width=20mm-6mm,minimum height=24.2mm-10mm,shape=document,inner sep=1ex,fill=white,drop shadow=gray!50},
            % tool/.style={rectangle, draw, fill=magenta!10, text width=3cm, minimum height=0.8cm, align=center, rounded corners},
            inv/.style={}
        ]

        % Input block
        \node[doc] (input) {Configuration\\[.2em]\textit{.yaml/.json/.py}};

### 2025-07-28 docs/paper/glossary.tex
feat: add case studies
chore: port content to new format
feat: add theory
feat: fast comment address
chore: add benchmark template

    first={Linear Programming (LP)},
    name={Linear Programming},

@@

            A Linear Programming problem is an optimization problem where the objective function and the constraints

@@

            A typical Linear Programming problem has the following form:

@@

>>>>

    first={Linear Program (LP)},
    name={Linear Program},

@@

            A Linear Program is an optimization problem where the objective function and the constraints

@@

            A typical Linear Program has the following form:

@@

\newglossaryentry{rkhs}{
    name={Reproducing Kernel Hilbert Space},
    text={RKHS},
    first={Reproducing Kernel Hilbert Space (RKHS)},
    firstplural={Reproducing Kernel Hilbert Spaces (RKHS)},
    description={}
\newglossaryentry{cbc}{
    name={Control Barrier Certificate},
    text={CBC},
    plural={CBCs},
    first={\emph{Control Barrier Certificate} (CBC)},
    firstplural={\emph{Control Barrier Certificates} (CBCs)},
    description={}
\newglossaryentry{cbf}{
    name={Control Barrier Certificate},
    text={CBF},
    plural={CBFs},
    first={\emph{Control Barrier Function} (CBF)},
    firstplural={\emph{Control Barrier Functions} (CBFs)},
    description={}
\newglossaryentry{gui}{
    name={Graphical User Interface},
    text={GUI},
    first={\emph{Graphical User Interface} (GUI)},
    description={}
\newglossaryentry{cli}{
    name={Command Line Interface},
    text={CLI},
    first={\emph{Command Line Interface} (CLI)},
    description={}
\newglossaryentry{nn}{
    name={Neural Network},
    text={NN},
    first={\emph{Neural Network} (NN)},
    description={}
\newglossaryentry{cme}{
    name={Conditional Mean Embedding},
    text={CME},
    plural={CMEs},
    first={\emph{Conditional Mean Embedding} (CME)},
    firstplural={\emph{Conditional Mean Embeddings} (CMEs)},
    description={}
